Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-11-19 scripts/MouseSexDiffVar_Oct_2020.Rmd
typo in Suppl Fig

plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing) #bind_rows

@@

overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #bind_rows

@@

plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all) #bind_rows

@@

plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing) #bind_rows

@@

overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #bind_rows

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #bind_rows

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) %>% 
  mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
# may require: 	
overall4.male.sigS$label <- "CI not overlapping zero"

>>>>

plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing) #use bind_rows in R3.6

@@

overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #use bind_rows in R3.6

@@

plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all) #use bind_rows in R3.6

@@

plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing) #use bind_rows in R3.6

@@

overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #use bind_rows in R3.6

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #use bind_rows in R3.6

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) %>% 
  mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
# R 3.6: do not use "%>% mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))"
overall4.male.sigS$label <- "CI not overlapping zero"
